The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-17 paper.tex
update

  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
  \citep{tseng2021} within the failed patch group when performing full-step updates,\
  new patches allocations, and ghost-zone interpolations.\
  In this way, we provide an elegant way to avoid the use of pressure/density floor,\
  being unnatural but widely used in almost publicly available codes.\

>>>>

  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
  \citep{tseng2021} within the failed patch group when performing full-step updates,\
  new patches allocations, and ghost-zone interpolations.\
  In this way, we provide an elegant approach to avoid the use of pressure/density floor,\
  being unnatural but widely used in almost publicly available codes.\
